---
title: "inundation_summary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{annual_plots}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, echo = FALSE, warning = FALSE, message = FALSE}
library(inundation)

```

These plots show the utility and explain the ecological relevance of the calc_summary function. The calc_summary function summarized the calc_inundation output over water year:

total_days_inund: total number of inundation days 
max_days_inund: maximum number of consecutive days of inundation 
first_date_inund: first date of inundation
last_date_inund: last date of inundation
last_date_overtopping: last date that the Fremont Weir was overtopped
number_overtopping_events: total number of inundation events

Note that total_days_inund will equal max_days_inund when there is a single inundation event within a water year. Also note that last_date_overtopping and last_date_inund may be equal when the floodplain drains quickly (e.g., there is no or limited western tributary input), and that the first_date_inund is also the first day of overtopping within a given water year because the calc_inundation function requires Fremont Weir overtopping to begin an inundation event. 

```{r, echo = FALSE, results = 'hide', message = FALSE}
#load data
inundation_summarised <- calc_summary()

```

The relationship between total_days_inund, max_days_inund and number_overtopping_events
```{r, echo = FALSE , warning = FALSE, message = FALSE}

plot(inundation_summarised$total_days_inund, inundation_summarised$max_days_inund, 
     cex = inundation_summarised$number_overtopping_events,
     xlab = "Total Days of Inundation per WY",
     ylab = "Max Number of Consecutive Days of Inundation per WY")

text(inundation_summarised$total_days_inund, inundation_summarised$max_days_inund-3, labels=inundation_summarised$water_year)

legend("topleft", "Point size is proportional to the Number of Events")
```
